Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-31 tex/paper.tex
save

\glnote{Extension to continuous nuisance parameters: have the adversary $r$
models the conditional distribution $p(z|f(X;\theta_f))$, e.g. with network
whose 2 outputs are parameters of a truncated gaussian and optimized such that
$p(z|f(X;\theta_f)) \approx N(\mu(f(X;\theta_f);\theta_r), \sigma(f(X;\theta_f);
\theta_r)$. The associated loss can be the likelihood (or?), which is maximal when the
approximation is perfect and minimal when the truncated gaussian degenerates to
a uniform (when $\sigma$ is large), in which case we should have the guarantee
that $f$ is pivotal.}

>>>>

\glnote{Extension to continuous nuisance parameters: have the adversary $r$
models the conditional distribution $p(z|f(X;\theta_f))$, e.g. with a network
whose 2 outputs are the parameters of a truncated gaussian and optimized such that
$p(z|f(X;\theta_f)) \approx N(\mu(f(X;\theta_f);\theta_r), \sigma(f(X;\theta_f);
\theta_r)$. The associated loss can be the likelihood (or?), which is maximal when the
approximation is perfect and minimal when the truncated gaussian degenerates to
a uniform (when $\sigma$ is large), in which case we should have the guarantee
that $f$ is pivotal.}
